GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-10-10 paper/kbanotebook2013/content/implementation.tex
integrated a bunch of changes, only integrated half of yangs changes

In this system, we use pattern matching methods to find corresponding slot 
values for entities. This is done by observing the training data which is the first four months of the corpus (October 2011 - February 2012). The procedure is: First Find stream items that contain the 
entities by using alias names of the entities. Then Inside these stream items, 
fetch the sentences which contain entities by using alias names and the 
coreference information provided by Lingpipe tags. Use these sentences to 
match existing patterns, and when patterns matched, generate SSF results.

Each pattern consists of five fields:

\begin{itemize}
\item Type of the entity
\item Slot name
\item Pattern content
\item Direction of the slot value to the entity
\item Type of the slot values
\end{itemize}

 When we match one pattern, we match all the 
fields except the third field, which is extracted as the final result.

 The type of slot values could be the entity 
type tagged by Lingpipe, noun phrase tagged by OpenNLP and the time phrases we 
hard-code. For these three kinds of patterns, we implement them in different 
ways accordingly. Next we will explain the patterns with more details, a brief
example can be found in Figure~\ref{fig:pattern}.

\textbf{Slot value type, tagged by Lingpipe:} For slot FounderOf, we have this
pattern: \textless \texttt{PER, FounderOf, founder, right, ORG}\textgreater. PER means 
that the entity we are finding slot values for is a PER entity; FounderOf 
means this is a pattern for FounderOf slot. Founder is the anchor word we are 
trying to match in the sentence text; right means that we are going to the 
right part of the sentence to match the pattern and find the slot value; ORG 
means the slot value should be a ORG entity.

\textbf{Slot value tagged as noun phrase by OpenNLP:} \textless \texttt{PER, AwardsWon, awarded, 
right, NP}\textgreater, NP meaning noun phrase. This pattern can be interpreted 
as that we are looking for a noun phrase after the “awarded'' since that noun 
phrase could possibly represent an award. Since titles and awards are usually 
not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the 
noun phrases.

\textbf{Slot value of time phrases, hard coded:} \textless \texttt{PER, DateOfDeath, died, right, 
last night}\textgreater. In this pattern, “last night'' means we are looking for 
exactly the phrase ``last night'' to the right of ``died''. This pattern is 
inspired by the intuition that in news articles, people often mention that 
somebody died last night instead of mentioning the accurate date information 
and Lingpipe tends not to tag phrases like ``last night'' as a DATE entity.

To improve recall, we introduce generic patterns that can generate many results.
But these patterns generate many errors, too. Thus there is a trade-off 
between the accuracy and recall. This is one drawback of using pattern 
matching method, meaning it is really hard to find good patterns with both 
high accuracy and recall.

For accuracy, we have found that there are three major kinds of errors: First,  
wrong entities found; next, wrong tags by the Lingpipe; and finally wrong results matched 
by the patterns. We solve the first problem by using the Wikipedia or twitter 
information of the entities to get better alias names. And we use
post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).

>>>>

In the data set, we are given 4 months of data (October 2011 - February 2012) as training data.
Instead of building a classifier we use pattern matching methods to find
corresponding slot values for entities. 
Pattern matching is simple to manipulate results and implement.
Additionally, we can simply to explain and evaluate results.

The procedure to extract slots with the patterns is to 
first find Streamitems that contain the 
entities by using alias names of the entities. Next, inside these Streamitems, 
fetch the sentences which contain entities by using alias names and the 
coreference information provided by Lingpipe tags. Use these sentences to 
match existing patterns, and when patterns matched, generate SSF results.

\begin{algorithm}
  \textbf{Given a set of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
  \textbf{Set of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
  \begin{algorithmic}[1]
    \FOR{$si \in \mathcal{S}$}
    \FOR{$s \in si$}
    \IF{$ check\_one\_of\_the\_patterns$}
    \STATE Emit(sentence, pattern)
  \ENDIF
\ENDFOR
\ENDFOR
\end{algorithmic}
\end{algorithm}

A pattern is defined as a record representing knowledge going to be added to a knowledge base.
A pattern $\mathcal{P}$ is represented as $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.

The first value, $p_1$ represents the type of entity. These entity types are in
the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC}
represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
represents a person.
The $p_2$ represents a slot name.
A list of slot names is present in Table~\ref{table:slotNameOntology}.
The third element $p_3$ is the pattern content. This is a string found in the sentence.
The extractor looks for this exact string or pattern in a sentence.
The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in
$p_4$ to explore sentence.
The final element $p_5$ represent the slot value of a pattern. Thois
%When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity 
type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. 
For these three kinds of patterns, we implement them in different 
ways accordingly. Next we will explain the patterns with more details, a brief
example can be found in Figure~\ref{fig:pattern}.

\textbf{Slot value type, tagged by Lingpipe:} For slot FounderOf, we have this
pattern: \textless \texttt{PER, FounderOf, ``founder'', right, ORG}\textgreater. PER means 
that the entity we are finding slot values for is a PER entity; FounderOf 
means this is a pattern for FounderOf slot. Founder is the anchor word we are 
trying to match in the sentence text; right means that we are going to the 
right part of the sentence to match the pattern and find the slot value; ORG 
means the slot value should be a ORG entity.

\textbf{Slot value tagged as noun phrase by OpenNLP:} \textless \texttt{PER, AwardsWon, ``awarded'', 
right, NP}\textgreater, NP meaning noun phrase. This pattern can be interpreted 
as that we are looking for a noun phrase after the ``awarded'' since that noun 
phrase could possibly represent an award. Since titles and awards are usually 
not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the 
noun phrases.

\textbf{Slot value of time phrases, hard coded:} \textless \texttt{PER, DateOfDeath, ``died'', right, 
``last night''}\textgreater. In this pattern, ``last night'' means we are looking for 
exactly the phrase ``last night'' to the right of ``died''. This pattern is 
inspired by the intuition that in news articles, people often mention that 
somebody died last night instead of mentioning the accurate date information 
and Lingpipe tends not to tag phrases like ``last night'' as a DATE entity.

We have found that there are three major classes of accuracy errors:
wrong entities found, wrong tags by the Lingpipe, and finally wrong results matched 
by the patterns. We solve the first problem by using the Wikipedia or twitter 
information of the entities to get better alias names. And we use
post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).

### 2013-10-10 paper/kbanotebook2013/content/introduction.tex
integrated a bunch of changes, only integrated half of yangs changes

We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
The data set from this task drop most our our design systems.
Overall, our contributions are the following:
\begin{itemize}[noitemsep,nolistsep]
\item we introduce a method to build models of name variations (Section~\ref{sec:preproc},~\ref{section:aliasgeneration});
\item we built a system to filter a large amount of diverse documents (Section~\ref{sec:ccr1},~\ref{sec:ccrimpl});
\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssf1},~\ref{sec:ssve});
\item we filter the final results using deduplication and inference (Section~\ref{sec:postproc},~\ref{section:highAccuracyFilter});
\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
\end{itemize}

\section{KBA Task Background\ceg{Move this to appendix?}}
\label{sec:kbatask}
The National Institute of Standards (NIST) hosted the
Text REtrieval Conference (TREC) --- Knowledge Base Acceleration challenge in 2013. The task
contains two main sections designed for this track, Cumulative Citation Recommendation 
and Streaming Slot Filling. Due to the importance of knowledge bases, both of these 
tracks aim to accelerating populating them, hence the title Knowledge Base Acceleration (KBA).
Below we describe each of these tracks and their purposes.

@@

For this track, assessors were instructed to ``use the Wikipedia article to 
identify (disambiguate) the entity, and then imagine forgetting all info in the WP 
article and asking whether the text provides any information about the entity'' \cite{JFrank12}.
Documents would be divided according to two metrics: a) mentioning the entity or 
not, b) relevance level to the entity:
\begin{itemize}
  \item \textbf{Mention} 
    \begin{itemize}
      \item \textbf{Mention:} Document explicitly mentions target entity, such as full 
        name, partial name, nickname, pseudonym, title, stage name.
      \item \textbf{Zero-mention:} Document does not directly mention target. Could 
        still be relevant, e.g.\ metonymic references like ``this administration'' --
        \textgreater ``Obama''. See also synecdoche. A document could also be relevant to 
        target entity through relation to entities mentioned in document -- apply this 
        test question: can I learn something from this document about target entity using 
        whatever other information I have about entity?
    \end{itemize}
  \item \textbf{Relevance}
    \begin{itemize}
      \item \textbf{Garbage:} not relevant, e.g.\ spam.
      \item \textbf{Neutral:} Not relevant, i.e.\ no info could be deduced about entity, 
        e.g., entity name used in product name, or only pertains to community of target 
        such that no information could be learned about entity, although you can see how 
        an automatic algorithm might have thought it was relevant.
      \item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive 
        implications, or topics or events of likely
        impact on entity.
      \item \textbf{Central:} Relates directly to target such that you would cite it in 
        the WP article for this entity, e.g.\ entity is a
        central figure in topics/events.

    \end{itemize}
\end{itemize}

>>>>

We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
The data set from this task drop most our our design systems.
Overall, our contributions are the following:
\begin{itemize}[noitemsep,nolistsep]
\item we introduce a method to build models of name variations (Section~\ref{section:aliasgeneration});
\item we built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
\item we filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
\end{itemize}

\section{KBA Task Background}
\label{sec:kbatask}
The National Institute of Standards (NIST) hosted the
Text REtrieval Conference (TREC) --- Knowledge Base Acceleration challenge in 2013. The task
contains two main sections designed for this track, Cumulative Citation Recommendation 
and Streaming Slot Filling. Due to the importance of knowledge bases, both of these 
tracks aim to accelerating populating them, hence the title Knowledge Base Acceleration (KBA).
Below we describe each of these tracks and their purposes.

@@

For this track, assessors were instructed to ``use the Wikipedia article to 
identify (disambiguate) the entity, and then imagine forgetting all info in the WP 
article and asking whether the text provides any information about the entity'' \cite{JFrank12}.
Documents are divided according if an entity is mentioned and a relevance level to the entity.

More specifically, a document may have a mention or be without a mention.
\begin{itemize}[noitemsep]
  \item \textbf{Mention:} Document explicitly mentions target entity, such as full 
    name, partial name, nickname, pseudonym, title, stage name.
  \item \textbf{Zero-mention:} Document does not directly mention target. Could 
    still be relevant, e.g.\ metonymic references like ``this administration'' 
    $\rightarrow$ ``Obama''. See also synecdoche. A document could also be relevant to 
    target entity through relation to entities mentioned in document -- apply this 
    test question: can I learn something from this document about target entity using 
    whatever other information I have about entity?
\end{itemize}

The relevance of a document to a query is split into the four classifications.
\begin{itemize}[noitemsep]
  \item \textbf{Garbage:} not relevant, e.g.\ spam.
  \item \textbf{Neutral:} Not relevant, i.e.\ no info could be deduced about entity, 
    e.g., entity name used in product name, or only pertains to community of target 
    such that no information could be learned about entity, although you can see how 
    an automatic algorithm might have thought it was relevant.
  \item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive 
    implications, or topics or events of likely
    impact on entity.
  \item \textbf{Central:} Relates directly to target such that you would cite it in 
    the WP article for this entity, e.g.\ entity is a
    central figure in topics/events.
\end{itemize}

### 2013-10-10 paper/kbanotebook2013/content/system.tex
integrated a bunch of changes, only integrated half of yangs changes

\begin{figure}
\centering
%\includegraphics[width=6in]{./images/sdl.eps}
\includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
% http://convert.neevia.com/pdfconvert/
\vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
\vspace*{-.2in}
\end{figure}

@@

In this section, we sketch out the main components of the system. Our system is 
built with a pipeline architecture in mind which gives it the advantage to run 
each section separately and allow stream processing without resources being wasted 
by one operation while others are awaiting (Figure~\ref{fig:system}).
This consists of a section to perform pre-processing to prepare the required data, 
Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming 
Slot Filling which generates the actual slot values and Post processing to 
increase precision/recall.

@@

\subsection{Preprocessing}
\label{sec:preproc}

To begin, we need to have real-world aliases of entities of interest. TREC KBA
prohibits Wikipedia entities to have any manual aliases being added and only
allows automatic ways. We use Wikipedia API backlink references
(redirects to a wiki entity) as aliases of the entity. We also extract 
aliases from within the text of a wiki entity, which will be described in
Section~\ref{section:aliasgeneration}. This whole process is referred to as
\textit{Alias Extraction}. On the other hand, regarding Twitter entities this
limit is lifted and participants are allowed to manually add aliases for them.
Part of the reason is that Twitter environment is composed of so much informal
and dialectic language which makes it extremely difficult to extract alias out
of tweets or entities descriptions in their profiles. This process of extracting
aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.

@@

\subsection{CCR}
\label{sec:ccr1}

The main goal of Cumulative Citation Recommendation is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching 
and treat all the documents that mention an entity equally likely to be citable. One of the reasons for this is 
that in former TREC KBA reports \cite{JFrank12} there were observations of how 
non-mentioning documents have a low chance of being citable in Wikipedia.
So we take on that and ignore non-citing documents.

@@

\subsection{SSF}
\label{sec:ssf1}
%\ceg{See the previous note.}
The purpose of slot filling is to extract proper values for relations of
interest, which can be found in Table~\ref{table:slotNameOntology}.
This is called Stream Slot Filling because data is being generated as time goes
on and for each extraction we should only consider current or past data.
In Figure~\ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}.
Stream slot filling is done by pattern matching documents with manually 
produced patterns for slots of interest. The way we do this is by observing a 
sentence that has a mention of the entity or one of its coreferences. An 
anchor word in the sentence related to the slot name is located and we match 
either left or right of the anchor word for potential slot values.

\subsection{Post Processing Algorithm}
\label{sec:postproc}

The SSF output of many extractions is noisy. The data contains duplicates and 
incorrect extractions. We can define rules to sanitize the output only using 
the information present in the SSF file. The file is processed in time order, 
in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
two classes of rules deduplication rules and inference rules. In our diagram we refer to this component as \textbf{High Accuracy Filter}.

>>>>

@@

In this section, we introduce the main components of the system. Our system is 
built with a pipeline architecture in mind giving it the advantage to run 
each section separately to allow stream processing without blocking the data flow of components 
(Figure~\ref{fig:system}).
The three logical components include sections for performing preprocessing to prepare the required data, 
Cumulative Citation Recommendation to annotate cite-worthy documents, Streaming 
Slot Filling to generate the actual slot values and PostProcessing to 
increase precision/recall. 
TREC provides a streaming data set and  entities from Twitter or WP to query.

@@

\begin{figure}
  \centering
%\includegraphics[width=6in]{./images/sdl.eps}
  \includegraphics[width=6in]{./images/sdl-eps-converted-to.pdf}
% http://convert.neevia.com/pdfconvert/
  \vspace*{-.1in} 
  \caption{The GatorDSR team System Architecture.
  Components are logically groups with dotted boxes.
  Color details the programing language implementation of components.}
  \label{fig:system}
  \vspace*{-.2in}
\end{figure}

\textbf{Preprocessing.}
\label{sec:preproc}
The contest prohibits Wikipedia entities to have any manual aliases being added and only
allows automatic ways. We use Wikipedia API backlink references
(redirects to a wiki entity) as aliases of the entity. We also extract 
aliases from within the text of a wiki entity, which will be described in
Section~\ref{section:aliasgeneration}. This whole process is referred to as
\textit{Alias Extraction}. 
The manual extraction rule is lifted and participants are allowed to manually add aliases for Twitter entities.
This is allowed because the Twitter website does not provide an example page from the beginning of the document stream.
This process of extracting
aliases for Twitter entities is referred to as \textit{Manual Alias Extraction}.

@@

\textbf{Cumulative Citation Recommendation.}
\label{sec:ccr1}
The main goal of CCR is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. We perform exact string matching 
and treat all the documents that mention an entity equally likely to be citable. One of the reasons for this is 
that in former TREC KBA reports \cite{JFrank12} there were observations of how 
non-mentioning documents have a low chance of being citable in Wikipedia.
So we take on that and ignore non-citing documents.

@@

\textbf{Streaming Slot Filling.}
\label{sec:ssf1}
%\ceg{See the previous note.}
The purpose of SSF is to extract proper values for relations of
interest, which can be found in Table~\ref{table:slotNameOntology}.
This is called Stream Slot Filling because data is being generated as time goes
on and for each extraction we should only consider current or past data.
In Figure~\ref{fig:system} we refer to this as \textit{Streaming Slot Value Extraction}.
Stream slot filling is done by pattern matching documents with manually 
produced patterns for slots of interest. The way we do this is by observing a 
sentence that has a mention of the entity or one of its coreferences. An 
anchor word in the sentence related to the slot name is located and we match 
either left or right of the anchor word for potential slot values.

\textbf{Post Processing Algorithm.}
\label{sec:postproc}
The SSF output of many extractions is noisy. The data contains duplicates and 
incorrect extractions. We can define rules to sanitize the output only using 
the information present in the SSF file. The file is processed in time order, 
in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
two classes of rules deduplication rules and inference rules. In our diagram we refer to this component as \textbf{High Accuracy Filter}.
